### 2012-02-07 contents.tex
Version submitted to MSR 2012.

	The experimental package is available at \url{https://sites.google.com/site/rodrigorgs2/msr2012}.

@@

	\begin{table}
		\begin{center}
		\caption{Verification techniques for all four subprojects.}
		\begin{tabular}{l|r|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering Testing} & 
			\textbf{\centering Inspection} & 
			\textbf{\centering Ad Hoc} \\
			\hline
			Eclipse/Platform        & 260 (1.1\%) & 524 (2.2\%) & 74 (0.3\%) \\
			Eclipse/EMF             & 27 (0.7\%) & 2 (0.1\%) & 0 (0.0\%) \\
			NetBeans/Platform       & 94 (0.6\%) & 5 (0.0\%) & 0 (0.0\%) \\
			NetBeans/VersionControl & 4 (0.1\%) & 1 (0.0\%) & 0 (0.0\%) 
			% \bottomrule
		\end{tabular}
		\end{center}

		\label{tab:how}
	\end{table}

@@

		\caption{Discovered QA team for all four subprojects.}
		\begin{tabular}{l|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering QA team size} & 
			\MyHead{2.5cm}{\textbf{\% of verifications by QA team}} \\
			\hline
			Eclipse/Platform        & 4 (2.4\%)  &  1.1\% \\
			Eclipse/EMF             & 0 (0.0\%)  &  0.0\% \\
			NetBeans/Platform       & 5 (21.7\%) & 93.3\% \\
			NetBeans/VersionControl & 5 (20.8\%) & 93.2\% \\
			% \bottomrule
		\end{tabular}
		\end{center}

		\label{tab:qa}
	\end{table}

@@

\begin{section}{Conclusion} \label{sec:conclusion}
	By analyzing four subprojects (two from Eclipse, two from NetBeans), we have found, using only data from bug repositories, subprojects with and without QA teams, with and without a well-defined verification phase. We also have found weaker evidence of the application of automated testing and source code inspection. Also, we have found cases in which marking a bug as \VERIFIED\ does not imply that any kind of software verification was actually performed.

>>>>

	The experimental package is available at \\ \url{https://sites.google.com/site/rodrigorgs2/msr2012}

@@

	\begin{table}
		\begin{center}
		\caption{Verification techniques for all four subprojects.} \label{tab:how}
		\begin{tabular}{l|r|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering Testing} & 
			\textbf{\centering Inspection} & 
			\textbf{\centering Ad Hoc} \\
			\hline
			Eclipse/Platform        & 260 (1.1\%) & 524 (2.2\%) & 74 (0.3\%) \\
			Eclipse/EMF             & 27 (0.7\%) & 2 (0.1\%) & 0 (0.0\%) \\
			NetBeans/Platform       & 94 (0.6\%) & 5 (0.0\%) & 0 (0.0\%) \\
			NetBeans/VersionControl & 4 (0.1\%) & 1 (0.0\%) & 0 (0.0\%) 
			% \bottomrule
		\end{tabular}
		\end{center}
	\end{table}

@@

		\caption{Discovered QA team for all four subprojects.} \label{tab:qa}
		\begin{tabular}{l|r|r}
			% \toprule
			\textbf{\centering Project} & 
			\textbf{\centering QA team size} & 
			\MyHead{2.5cm}{\textbf{\% of verifications by QA team}} \\
			\hline
			Eclipse/Platform        & 4 (2.4\%)  &  1.1\% \\
			Eclipse/EMF             & 0 (0.0\%)  &  0.0\% \\
			NetBeans/Platform       & 5 (21.7\%) & 93.3\% \\
			NetBeans/VersionControl & 5 (20.8\%) & 93.2\% \\
			% \bottomrule
		\end{tabular}
		\end{center}

	\end{table}

@@

\begin{section}{Conclusion} \label{sec:conclusion}
	By analyzing four subprojects (two from Eclipse, two from NetBeans), we have found, using only data from bug repositories, subprojects with and without QA teams, with and without a well-defined verification phase. We also have found weaker evidence of the application of automated testing and source code inspection. Also, there were cases in which marking a bug as \VERIFIED\ did not imply that any kind of software verification was actually performed.
